Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
Changes order of object storage discussion

@@

@@

In order to reduce load on the monitoring service, Ceph OSDs use a gossip
protocol to efficiently propagate changes to cluster maps throughout the
system, and automonmously initiate recovery mechansims when failures are
discovered.

@@

\paragraph*{Malacology:} Map modification for propogation of state. We allow applications to augment
these data structures with application-specific metdata. In order to keep the
size of these data structures small application state may be stored elsewhere
and the references stored within the data structure.

Allowing users to define custom code that executes in the storage nodes is a 
useful technique for offloading computation closer to where the data is stored 
in order to significantly reduce the amount of data moved between storage 
servers and clients. Ceph provides a rich plugin framework for defining new 
interfaces to objects
stored within RADOS, effectively allowing developers to use co-design
techniques to define logical storage devices tailored to their application
domain.

>>>>

There are multiple reasons that make Lua an attractive runtime for implementing 
Malacology. Lua is a portable, embedded
scripting language that offers superious performance and productivity
trade-offs, including a JIT-based implementation that is well known for near
native performance. Additionally, Lua has been used extensively in game engines, 
and systems research \cite{neto:dls14-luaos}, including storage systems where it 
has been effectively used both on
\cite{grawinkel:pdsw2012-lua,watkins2013:bdmc13-in-vivo,geambasu_comet_2010} and 
off
\cite{sevilla:sc15-mantle} the performance critical path. Finally, the 
flexibility of the runtime allows to sandbox applications in order to address 
security and performance concerns.

@@

Allowing users to define custom code that executes in the storage nodes is a 
useful technique for offloading computation closer to where the data is stored 
in order to significantly reduce the amount of data moved between storage 
servers and clients.
Ceph provides object storage via 
RADOS~\cite{weil_rados_2007}, the reliable distributed object store. 
Ceph provides a rich plugin framework for defining new interfaces to objects
stored within RADOS, effectively allowing developers to use co-design
techniques to define logical storage devices tailored to their application
domain.

@@

In order to reduce load on the monitoring service, Ceph OSDs use a gossip
protocol to efficiently propagate changes to cluster maps throughout the
system, and autonomously initiate recovery mechanisms when failures are
discovered.

@@

\paragraph*{Malacology:} Map modification for propogation of state. We allow applications to augment
these data structures with application-specific metadata. In order to keep the
size of these data structures small application state may be stored elsewhere
and the references stored within the data structure.
